ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-26 paper/appendix.tex
ss

\begin{figure}
  \centering
  \includegraphics[width=0.75\linewidth]{../artifacts/results/images/mnist_generated_JEM Ensemble.png}
  \caption{Conditionally generated \textit{MNIST} images for our JEM Ensemble.}\label{fig:mnist-gen}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{../artifacts/results/images/moons_generated_JEM.png}
  \caption{Conditionally generated samples (stars) for our \textit{Moons} data using a JEM.}\label{fig:moons-gen}
\end{figure}
\subsubsection{Inference: Quantifying Models' Generative Property}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{../artifacts/results/images/poc_set_size.png}
  \caption{Prediction set size (left), smooth set size loss (centre) and configurable classification loss (right) for a JEM trained on our \textit{Linearly Separable} data.}\label{fig:cp-diff}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.75\linewidth]{../www/mnist_generated_JEM Ensemble.png}
  \caption{Conditionally generated \textit{MNIST} images for our JEM Ensemble.}\label{fig:mnist-gen}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{../www/moons_generated_JEM.png}
  \caption{Conditionally generated samples (stars) for our \textit{Moons} data using a JEM.}\label{fig:moons-gen}
\end{figure}
\subsubsection{Inference: Quantifying Models' Generative Property}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{../www/poc_set_size.png}
  \caption{Prediction set size (left), smooth set size loss (centre) and configurable classification loss (right) for a JEM trained on our \textit{Linearly Separable} data.}\label{fig:cp-diff}
\end{figure}
